On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-21 Manuscript/manuscript.tex
smoothed intro

Block bootstrap is a tool to construct confidence intervals (CI)
to make inferences about dependent data. Early ideas were developed
independently by 
\citet{hall1985resampling, carlstein1986use,kunsch1989jackknife}.
It has since been applied in various fields such as econometrics
\citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}.
Block bootstrap is useful for serially dependent
data when the serial dependence is not specified or not of primary interest.
The method is expected to produce CIs with coverage rates
matching their nominal levels as the sample size grows. However,
when dealing with finite sample sizes, an important question is how large the
sample size must be for block bootstrap CIs to have the
desired coverage rates.

\jy{too wordy; do some condensing} \mc{condensed a little bit}
The performance of bootstrap standard errors with independent data
in providing valid uncertainty measures has been extensively studied.
For example, for non-block bootstrap, \citet{hesterberg2015teachers} notes
that while percentile-based CIs for the mean from nonparametric bootstrap
are more accurate than $t$-intervals for larger sample sizes, they are
less accurate for smaller sample sizes. \citet{chernick2009revisiting} finds 
that the best method to estimate
the parameter of a distribution depends on the sample size, the number of
bootstrap resamples, and the confidence level. In the context of structural
equation modeling, \citet{nevitt2001performance} find
that a sample size of 200--1000 is sufficient for interval estimation
using standard nonparametric bootstrap. In estimating the proportion of 
variation attributable to a certain variable, \citet{burch2012nonparametric} finds
that three nonparametric bootstrap methods (standard, percentile, and 
bias-corrected
and accelerated) approach the coverage of a pivotal quantity as the sample size
gets larger for an underlying normal distribution, but for other distributions, 
coverage may deteriorate as the sample size increases.
When attempting to create interval estimations for the Pearson correlation 
coefficient of bivariate normal data, \citet{puth2015variety} find bootstrap 
methods to be less accurate than the Fisher's transformation method even 
for a sample with size~$100$ and correlation coefficient equal to 0.
The general consensus is that a big sample size is necessary.

Few studies have provided a practical guide on what size is needed
for block bootstrap inference for dependent data.
In a linear regression setting with dependent data where the
regression errors are generated from a homoscedastic AR(1) process, 
\citet{goncalves2005bootstrap} find that the standard error estimates from
moving block bootstrap in small samples may be more accurate than those
from closed-form asymptotic estimates, but moving block bootstrap 
CIs still do not have sufficient coverage of the target parameter even for
sample size~$1024$.

@@

\jy{Practice my writing style guidelines. Use two blank lines to separate
  paragraphs.} \mc{addressed}

@@

\paragraph{A Proposed CI}
We propose a CI that is centered at the point estimator and uses the variation
in the bootstrap estimates to construct the error bound. This interval requires
the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$.
A $(1 - \alpha)100\%$ CI is
\[
(\hat\theta_{n, \alpha/2}^{(b)} - \widehat{\text{bias}}, \quad
\hat\theta_{n, 1 - \alpha/2}^{(b)} - \widehat{\text{bias}}).
\]
This CI is centered around $\hat\theta_n$ and can also be rewritten
as 
\[
(\hat\theta_n + \hat\theta_{n, \alpha/2}^{(b)} - \bar\theta_n^{(b)}, \quad
\hat\theta_n + \hat\theta_{n, 1 - \alpha/2}^{(b)} - \bar\theta_n^{(b)}).
\]
It is asymmetric, as different critical values are used to compute
the lower and upper bounds.
\jy{Double check} \mc{changed BCA, had to rerun simulations because I did k
degrees of freedom instead of k - 1}

>>>>

Block bootstrap is a tool to construct confidence intervals (CI)
to make inferences about dependent data. Essentially, it depends on correct
estimation of the uncertainty in the estimation. Early ideas were developed
by \citet{hall1985resampling, carlstein1986use,kunsch1989jackknife}.
It has since been applied in various fields, for instance, econometrics
\citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}.
Block bootstrap is especially useful for serially dependent
data when the serial dependence is not specified or not of primary interest.
The method is expected to produce CIs with coverage rates
matching their nominal levels as the sample size grows. However,
when dealing with finite sample sizes, an important question is how large the
sample size must be for block bootstrap CIs to have the
desired coverage rates.

For independent data, extensive research has explored the effectiveness of
bootstrap standard errors in providing accurate uncertainty measures.
For example, \citet{hesterberg2015teachers} observes
that while percentile-based CIs for the mean parameter
are more accurate than $t$-intervals for larger sample sizes, they accuracy
diminishes for smaller sample sizes. The optimal parameter estimation of a
distribution, according to \citet{chernick2009revisiting},
depends on the sample size, the number of
bootstrap replicates, and the confidence level. In structural
equation modeling, \citet{nevitt2001performance} find
that a sample size of 200--1000 is sufficient for interval estimation
using standard nonparametric bootstrap. Estimating variance component,
\citet{burch2012nonparametric} report that as the sample size increases under a
normal distribution, nonparametric bootstrap methods approach the coverage of a
pivotal quantity as the sample size, but for other distributions, the coverage
can deteriorate. In estimating the correlation coefficient of bivariate normal
data, \citet{puth2015variety} note that even for a sample size of~$100$ with
true correlation coefficient~0, bootstrap methods are less accurate than the
Fisher's transformation. The prevailing consensus highlights the necessity of a
substantial sample size for bootstrap CIs to attain the desired coverage.

Limited research has offered practical guidance concerning the requisite sample
size for employing block bootstrap inference with dependent data. In the context
of linear regression involving dependent data, where regression errors stem from
a homoscedastic autoregressive process of order-1, the investigation conducted
by \citet{goncalves2005bootstrap} reveals that, in cases of small sample sizes,
standard error estimates derived from the moving block bootstrap approach may
demonstrate greater accuracy than those based on closed-form asymptotic
estimates. Nonetheless, even when considering a substantial sample size of
~$1024$, confidence intervals generated through the moving block bootstrap
method still fail to adequately encompass the target parameter. The scarcity of
existing literature addressing the necessary sample sizes conducive to the
efficacy of block bootstrap techniques has spurred the initiation of the present
study.

@@

@@

\paragraph{A Proposed CI}
We propose a CI that is centered at the point estimator and uses the variation
in the bootstrap estimates to construct the error bound. This interval requires
the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$.
A $(1 - \alpha)100\%$ CI is
\[
(\hat\theta_{n, \alpha/2}^{(b)} - \widehat{\text{bias}}, \quad
\hat\theta_{n, 1 - \alpha/2}^{(b)} - \widehat{\text{bias}}).
\]
This CI is centered around $\hat\theta_n$ and can also be rewritten
as 
\[
(\hat\theta_n + \hat\theta_{n, \alpha/2}^{(b)} - \bar\theta_n^{(b)}, \quad
\hat\theta_n + \hat\theta_{n, 1 - \alpha/2}^{(b)} - \bar\theta_n^{(b)}).
\]
It is asymmetric, as different critical values are used to compute
the lower and upper bounds.
